Exploring dimensions of biodiversity in Japanese ferns

### 2020-07-14 ms/manuscript.Rmd
Fix theme calls in ms

```{r richness, width = 7, height = 4}
# Richness
a <- ggplot(ses_div_ferns_spatial, aes(fill = richness)) +
  geom_sf(color = "transparent") +
  scale_fill_scico(palette = "lajolla") + 
  labs(fill = "Richness") +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  map_theme

# Sampling rendundancy
b <- ggplot(ses_div_ferns_spatial, aes(fill = redundancy)) +
  geom_sf(color = "transparent") +
  scale_fill_scico(palette = "lajolla") + 
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  labs(fill = "Redundancy") +
  map_theme +
  theme(
    axis.text.y = element_blank()
  )

@@

```{r diversity, fig.width = 7, fig.height = 9}
# PD
a <- ggplot(ses_div_ferns_spatial, aes(fill = pd_obs)) +
  geom_sf(color = "transparent") +
  labs(fill = "PD") +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  scale_fill_scico(palette = "lajolla") + 
  map_theme +
  theme(
    axis.text.x = element_blank()
  )

# SES of PD
b <- ggplot(ses_div_ferns_spatial, aes(fill = pd_obs_z)) +
  geom_sf(color = "transparent") +
  labs(fill = "SES PD") +
  scale_fill_scico(
    palette = "romaO",
    na.value="grey80",
    direction = -1,
    limits = c(
      -get_limit(ses_div_ferns_spatial, pd_obs_z, "abs"),
      get_limit(ses_div_ferns_spatial, pd_obs_z, "abs")
    )) +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  map_theme +
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_blank()
  )

# RPD
c <- ggplot(ses_div_ferns_spatial, aes(fill = rpd_obs)) +
  geom_sf(color = "transparent") +
  labs(fill = "RPD") +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  scale_fill_scico(palette = "lajolla") + 
  map_theme +
  theme(
    axis.text.x = element_blank()
  )

# SES of RPD
d <- ggplot(ses_div_ferns_spatial, aes(fill = rpd_obs_z)) +
  geom_sf(color = "transparent") +
  labs(fill = "SES RPD") +
  scale_fill_scico(
    palette = "roma",
    na.value="grey80",
    direction = -1,
    limits = c(
      -get_limit(ses_div_ferns_spatial, rpd_obs_z, "abs"),
      get_limit(ses_div_ferns_spatial, rpd_obs_z, "abs")
    )) +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  # highlight only significant cells
  # gghighlight(pd_obs_p > 0.975 | pd_obs_p < 0.025) +
  map_theme +
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_blank()
  )

# FD
e <- ggplot(ses_div_ferns_spatial, aes(fill = fd_obs)) +
  geom_sf(color = "transparent") +
  labs(fill = "FD") +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  scale_fill_scico(palette = "lajolla") + 
  map_theme +
  theme(
    axis.text.x = element_blank()
  )

# SES of FD
f <- ggplot(ses_div_ferns_spatial, aes(fill = fd_obs_z)) +
  geom_sf(color = "transparent") +
  labs(fill = "SES FD") +
  scale_fill_scico(
    palette = "roma",
    na.value="grey80",
    direction = -1,
    limits = c(
      -get_limit(ses_div_ferns_spatial, fd_obs_z, "abs"),
      get_limit(ses_div_ferns_spatial, fd_obs_z, "abs")
    )) +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  # highlight only significant cells
  # gghighlight(mpd_morph_obs_p > 0.975 | mpd_morph_obs_p < 0.025) +
  map_theme +
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_blank()
  )

# RFD
g <- ggplot(ses_div_ferns_spatial, aes(fill = rfd_obs)) +
  geom_sf(color = "transparent") +
  labs(fill = "RFD") +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  scale_fill_scico(palette = "lajolla") + 
  map_theme

# SES of RFD
h <- ggplot(ses_div_ferns_spatial, aes(fill = rfd_obs_z)) +
  geom_sf(color = "transparent") +
  labs(fill = "SES RFD") +
  scale_fill_scico(
    palette = "roma",
    na.value="grey80",
    direction = -1,
    limits = c(
      -get_limit(ses_div_ferns_spatial, rfd_obs_z, "abs"),
      get_limit(ses_div_ferns_spatial, rfd_obs_z, "abs")
    )) +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  # highlight only significant cells
  # gghighlight(rfd_obs_p > 0.975 | rfd_obs_p < 0.025) +
  map_theme +
  theme(
    axis.text.y = element_blank()
  )

@@

```{r endemism, fig.width = 7, fig.height = 8}
# PE
a <- ggplot(ses_div_ferns_spatial, aes(fill = pe_obs)) +
  geom_sf(color = "transparent") +
  scale_fill_scico(palette = "lajolla") + 
  labs(fill = "PE") +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  map_theme +
  theme(
    axis.text.x = element_blank()
  )

# PE rank
b <- ggplot(ses_div_ferns_spatial, aes(fill = pe_obs_rank)) +
  geom_sf(color = "transparent") +
  labs(fill = "Rank PE") +
  scale_fill_scico(palette = "lajolla") +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  map_theme +
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_blank()
  )

# RPE
c <- ggplot(ses_div_ferns_spatial, aes(fill = rpe_obs)) +
  geom_sf(color = "transparent") +
  scale_fill_scico(palette = "lajolla") +
  labs(fill = "RPE") +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  map_theme +
  theme(
    axis.text.x = element_blank()
  )

# SES RPE
d <- ggplot(ses_div_ferns_spatial, aes(fill = rpe_obs_z)) +
  geom_sf(color = "transparent") +
  labs(fill = "SES RPE") +
  scale_fill_scico(
    palette = "roma",
    na.value="grey80",
    direction = -1,
    limits = c(
      -get_limit(ses_div_ferns_spatial, rpe_obs_z, "abs"),
      get_limit(ses_div_ferns_spatial, rpe_obs_z, "abs")
    )) +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  map_theme +
  theme(
    axis.text.y = element_blank()
  )

@@

e <- 
  ses_div_ferns_spatial %>%
  mutate(endem_type = replace_na(endem_type, "none")) %>%
  ggplot(aes(fill = endem_type)) +
  geom_sf(color = "transparent") +
  labs(fill = "Endemism\ntype") +
  scale_fill_manual(values = canape_cols, breaks = c("neo", "paleo", "mixed", "none"), labels = c("Neo", "Paleo", "Mixed", "Not endemic")) + 
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  map_theme_light

@@

```{r bioregions, fig.width = 7, fig.height = 3}
# Taxonomic bioregions
a <- ggplot(ses_div_ferns_spatial, aes(fill = taxonomic_cluster)) +
  geom_sf(color = "transparent") +
  scale_fill_carto_d(name = "Cluster", type = "qualitative", palette = "Bold") +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  map_theme_light

# Phylogenetic bioregions
b <- ggplot(ses_div_ferns_spatial, aes(fill = phylo_cluster)) +
  geom_sf(color = "transparent") +
  labs(fill = "Cluster") +
  scale_fill_carto_d(name = "Cluster", type = "qualitative", palette = "Bold") +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  map_theme_light

>>>>

```{r richness, width = 7, height = 4}
# Richness
a <- ggplot(ses_div_ferns_spatial, aes(fill = richness)) +
  geom_sf(color = "transparent") +
  scale_fill_scico(palette = "lajolla") + 
  labs(fill = "Richness") +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  map_theme()

# Sampling rendundancy
b <- ggplot(ses_div_ferns_spatial, aes(fill = redundancy)) +
  geom_sf(color = "transparent") +
  scale_fill_scico(palette = "lajolla") + 
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  labs(fill = "Redundancy") +
  map_theme() +
  theme(
    axis.text.y = element_blank()
  )

@@

```{r diversity, fig.width = 7, fig.height = 9}
# PD
a <- ggplot(ses_div_ferns_spatial, aes(fill = pd_obs)) +
  geom_sf(color = "transparent") +
  labs(fill = "PD") +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  scale_fill_scico(palette = "lajolla") + 
  map_theme() +
  theme(
    axis.text.x = element_blank()
  )

# SES of PD
b <- ggplot(ses_div_ferns_spatial, aes(fill = pd_obs_z)) +
  geom_sf(color = "transparent") +
  labs(fill = "SES PD") +
  scale_fill_scico(
    palette = "romaO",
    na.value="grey80",
    direction = -1,
    limits = c(
      -get_limit(ses_div_ferns_spatial, pd_obs_z, "abs"),
      get_limit(ses_div_ferns_spatial, pd_obs_z, "abs")
    )) +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  map_theme() +
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_blank()
  )

# RPD
c <- ggplot(ses_div_ferns_spatial, aes(fill = rpd_obs)) +
  geom_sf(color = "transparent") +
  labs(fill = "RPD") +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  scale_fill_scico(palette = "lajolla") + 
  map_theme() +
  theme(
    axis.text.x = element_blank()
  )

# SES of RPD
d <- ggplot(ses_div_ferns_spatial, aes(fill = rpd_obs_z)) +
  geom_sf(color = "transparent") +
  labs(fill = "SES RPD") +
  scale_fill_scico(
    palette = "roma",
    na.value="grey80",
    direction = -1,
    limits = c(
      -get_limit(ses_div_ferns_spatial, rpd_obs_z, "abs"),
      get_limit(ses_div_ferns_spatial, rpd_obs_z, "abs")
    )) +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  # highlight only significant cells
  # gghighlight(pd_obs_p > 0.975 | pd_obs_p < 0.025) +
  map_theme() +
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_blank()
  )

# FD
e <- ggplot(ses_div_ferns_spatial, aes(fill = fd_obs)) +
  geom_sf(color = "transparent") +
  labs(fill = "FD") +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  scale_fill_scico(palette = "lajolla") + 
  map_theme() +
  theme(
    axis.text.x = element_blank()
  )

# SES of FD
f <- ggplot(ses_div_ferns_spatial, aes(fill = fd_obs_z)) +
  geom_sf(color = "transparent") +
  labs(fill = "SES FD") +
  scale_fill_scico(
    palette = "roma",
    na.value="grey80",
    direction = -1,
    limits = c(
      -get_limit(ses_div_ferns_spatial, fd_obs_z, "abs"),
      get_limit(ses_div_ferns_spatial, fd_obs_z, "abs")
    )) +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  # highlight only significant cells
  # gghighlight(mpd_morph_obs_p > 0.975 | mpd_morph_obs_p < 0.025) +
  map_theme() +
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_blank()
  )

# RFD
g <- ggplot(ses_div_ferns_spatial, aes(fill = rfd_obs)) +
  geom_sf(color = "transparent") +
  labs(fill = "RFD") +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  scale_fill_scico(palette = "lajolla") + 
  map_theme()

# SES of RFD
h <- ggplot(ses_div_ferns_spatial, aes(fill = rfd_obs_z)) +
  geom_sf(color = "transparent") +
  labs(fill = "SES RFD") +
  scale_fill_scico(
    palette = "roma",
    na.value="grey80",
    direction = -1,
    limits = c(
      -get_limit(ses_div_ferns_spatial, rfd_obs_z, "abs"),
      get_limit(ses_div_ferns_spatial, rfd_obs_z, "abs")
    )) +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  # highlight only significant cells
  # gghighlight(rfd_obs_p > 0.975 | rfd_obs_p < 0.025) +
  map_theme() +
  theme(
    axis.text.y = element_blank()
  )

@@

```{r endemism, fig.width = 7, fig.height = 8}
# PE
a <- ggplot(ses_div_ferns_spatial, aes(fill = pe_obs)) +
  geom_sf(color = "transparent") +
  scale_fill_scico(palette = "lajolla") + 
  labs(fill = "PE") +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  map_theme() +
  theme(
    axis.text.x = element_blank()
  )

# PE rank
b <- ggplot(ses_div_ferns_spatial, aes(fill = pe_obs_rank)) +
  geom_sf(color = "transparent") +
  labs(fill = "Rank PE") +
  scale_fill_scico(palette = "lajolla") +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  map_theme() +
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_blank()
  )

# RPE
c <- ggplot(ses_div_ferns_spatial, aes(fill = rpe_obs)) +
  geom_sf(color = "transparent") +
  scale_fill_scico(palette = "lajolla") +
  labs(fill = "RPE") +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  map_theme() +
  theme(
    axis.text.x = element_blank()
  )

# SES RPE
d <- ggplot(ses_div_ferns_spatial, aes(fill = rpe_obs_z)) +
  geom_sf(color = "transparent") +
  labs(fill = "SES RPE") +
  scale_fill_scico(
    palette = "roma",
    na.value="grey80",
    direction = -1,
    limits = c(
      -get_limit(ses_div_ferns_spatial, rpe_obs_z, "abs"),
      get_limit(ses_div_ferns_spatial, rpe_obs_z, "abs")
    )) +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  map_theme() +
  theme(
    axis.text.y = element_blank()
  )

@@

e <- 
  ses_div_ferns_spatial %>%
  mutate(endem_type = replace_na(endem_type, "none")) %>%
  ggplot(aes(fill = endem_type)) +
  geom_sf(color = "transparent") +
  labs(fill = "Endemism\ntype") +
  scale_fill_manual(values = canape_cols, breaks = c("neo", "paleo", "mixed", "none"), labels = c("Neo", "Paleo", "Mixed", "Not endemic")) + 
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  map_theme_light()

@@

```{r bioregions, fig.width = 7, fig.height = 3}
# Taxonomic bioregions
a <- ggplot(ses_div_ferns_spatial, aes(fill = taxonomic_cluster)) +
  geom_sf(color = "transparent") +
  scale_fill_carto_d(name = "Cluster", type = "qualitative", palette = "Bold") +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  map_theme_light()

# Phylogenetic bioregions
b <- ggplot(ses_div_ferns_spatial, aes(fill = phylo_cluster)) +
  geom_sf(color = "transparent") +
  labs(fill = "Cluster") +
  scale_fill_carto_d(name = "Cluster", type = "qualitative", palette = "Bold") +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  map_theme_light()
